---
title: "Coronavirus Historical Data - China and its provinces"
author: "Adela Sobotkova"
date: "18 March 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Part II — Historical Data

Part One was only able to show the newest and latest data, but what most people are really concerned about are the daily historical data, the so called time-series.
What if you want to analyze some detailed historical data? Fear not, 'r load_nCov2019()' is here to the rescue.

```{r historical, warning=FALSE}
library(nCov2019)
y <- load_nCov2019(lang='en')
y
# nCov2019 historical data 
# last update: 2020-02-07
```

## Historical Data for China
Using the same method as 'r get_nCov2019()' , we can query all provincial detailed data using []

```{r historical China}
head(y[c(1:6, 9:11)])
```

We can just select the cumulative and newly added data. The relevant columns are 'r province, city, time, cum_confirm, cum_heal, cum_dead, confirm, dead, heal' , so 'r x['Hubei', c(1:6,9:11)]' is sufficient.

## Provincial & City Details in China
Similar to the above, if you wanted to dig deeper to get provincial-specific data, then you just need to include the province name:
```{r historical Chinese provinces}
head(y['Hubei',]) # replace Hubei with any province
```


If you want to dig even deeper into city-specific data, then you can specify a city within the province. For example, if you wanted to look at the data for Wuhan, you would do the following:
```{r historical Chinese cities}
head(subset(y['Hubei',], city == "Wuhan"))
```

You can then use this data for visualizations. For example:

# Plot individual cities
Here is a nice plot showing the rates of confirmed case in individual cities in the Anhui province. 'r ggrepel' makes sure the labels are not cluttered and read nicely. 
```{r plot historical Chinese cities}
library(ggplot2)
require(ggrepel)
d <- y['Anhui',] # replace Anhui with any province
ggplot(d, aes(time, as.numeric(cum_confirm), group=city, color=city)) +
  geom_point() + geom_line() +
  geom_label_repel(aes(label=city), data=d[d$time == time(y), ], hjust=1) +
  theme_minimal(base_size = 14) + theme(legend.position='none') +
  xlab(NULL) + ylab(NULL)
```

# Summary Results of China
Similar to 'r get_nCov2019()' , you are also able to call the 'r summary()' function on the historical data.
```{r summary}
head(summary(y)[,1:5])
```

Here's another quick visualisation of historical trends per province
```{r}
ggplot(summary(y, 'Hubei'), aes(time, as.numeric(cum_confirm))) +
  geom_col()
```
or city-specific
```{r}
ggplot(subset(y['Hubei',], city == "Huanggang"), aes(time, as.numeric(cum_confirm))) + geom_col()
```



# Bibliography and other resources
If you use 'r nCov2019' package, please cite the following preprint:

Tianzhi Wu, Erqiang Hu, Xijin Ge*, Guangchuang Yu*. Open-source analytics tools for studying the COVID-19 coronavirus outbreak. medRxiv, 2020.02.25.20027433. doi: https://doi.org/10.1101/2020.02.25.20027433